---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# csdm

<!-- badges: start -->
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT/)
[![R-CMD-check](https://github.com/pedersen-fisheries-lab/csdm/workflows/R-CMD-check/badge.svg)](https://github.com/pedersen-fisheries-lab/csdm/actions)
[![Codecov test coverage](https://codecov.io/gh/pedersen-fisheries-lab/csdm/branch/main/graph/badge.svg)](https://app.codecov.io/gh/pedersen-fisheries-lab/csdm)
[![Downloads](https://cranlogs.r-pkg.org/badges/csdm?color=brightgreen)](https://CRAN.R-project.org/package=csdm/)
[![Latest Release](https://img.shields.io/github/v/release/pedersen-fisheries-lab/csdm?label=Latest%20Release)](https://github.com/pedersen-fisheries-lab/csdm/releases/latest)
[![CRAN Version](https://img.shields.io/cran/v/csdm?label=CRAN%20Version)](https://CRAN.R-project.org/package=csdm)
[![GitHub Version](https://img.shields.io/github/r-package/v/pedersen-fisheries-lab/csdm?label=GitHub%20Version)](https://github.com/pedersen-fisheries-lab/csdm/blob/main/DESCRIPTION)
<!-- badges: end -->

<!-- badges: end -->

The goal of csdm is to implement a bayesian catch saturation-depletion model.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("pedersen-fisheries-lab/csdm")
```
## Example

1. Let's use the data provided in the package and taken from Delury's population
estimator data.

```{r}
library(csdm)
delury <- csdm::delury_lobster
```

2. Let's run the model.

```{r}
delury_model <- csdm(catch = cpue,
                     effort = traps,
                     biomass = ~1,
                     q = ~1,
                     s = ~1,
                     data = delury,
                     prior = list(B0_logmean_prior_sd = log(1000),
                                  B0_group_prior_logsd = log(100)),
                     upper =  c(B0 = 1e10, q = 1e-3, s = 100),
                     chains = 4,
                     iter = 1000)
```

3. You can extract the fit for cpue, as well as the biomass estimate.

```{r}
get_cpue_fit(delury_model)
```

```{r}
get_biomass(delury_model)
```

4. You can also get default plots for cpue and biomass.

```{r}
plot(delury_model)
```
```{r}
plot_biomass(delury_model)
```
